Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-01 paper/lncsFormat.tex
finish 3.3.1

The transfer learning based event detection method \textsc{LTDetector} also coincides with the news value theory\cite{caple2013delving}, which emphasizes the \textit{news unexpectedness} -- ``the unpredictable or the rare is more newsworthy than the routine"\cite{bell1991language}.
Following this guideline, if the journalist knew the history states, aka, the ``routine things" of everyday better, he/she would tend to choose more unexpected news to report.

@@

@@

\subsection{Detecting Events from Recent States}
\label{subsec:detection}
Given the words' accurate meaning, events are  detected accurately as the patterns of words' time series are better exposed.
Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw time series.
%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.

We take the detection in three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
%这里添加对这几个Definition的解释。

\begin{comment}
\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
\end{rmk}
\end{comment}

For a specific word \(w\) and the category \(c\), as stream states have provided the time series \(\{n(c,t_{1},w^{(c)}), \cdots, n(c,t_{T},w^{(c)})\}\), many bursty detection methods on the time series can be applied to check if the word \(w\) is bursty in category \(c\).  
%Text stream evolves more quickly with time than knowledge base.
%For example, recent state of Military contain .
%In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。

>>>>

@@

\begin{rmk}[Event Related Articles] Event related articles \(\mathcal{D}_{c,t,i}\) are articles that relate to the \(i\)-th event in time \(t\) under the category \(c\), and correspond to the event phase \(\mathcal{C}_{c,t,i}\).
\end{rmk}

@@

\subsection{Detecting Events from Recent States}
\label{subsec:detection}
After transfer learning, events are detected accurately because the word time series is refined as multiple corresponding (word, category) time series, and the bursty pattern is better exposed. 
Taking the word \textit{hood} as an example, it belongs to the category \textit{Military} when it appeared in \textit{Ft Hood}, a US military establishment located in Texas.
As shown in Figure \ref{fig:hood}, the bursty pattern of \textit{hood} is clearly exposed after distinguishing its \textit{Military} time series from the raw one.
%Therefore, the processing on each category's accurate stream states leads to the accurate event detection.

Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
%这里添加对这几个Definition的解释。

\textbf{Detecting events' candidate words}. For a word \(w\) and a category \(c\), on its time series \(\{n(c,t,w^{(c)})\}_{t=1}^{T}\), many bursty detection methods can be applied to check if the word \(w\) is bursty in category \(c\) by given time \(t\). 
We assume the document frequency of \(w^{(c)}\) follows a poisson distribution, which is also used in \cite{Diao:2012wj}.
And the document frequency of nonbursting \(w^{(c)}\) has the possison distribution with the parameter \(\lambda=\mu_0\); while the bursting one with the parameter \(4\mu_0\) means the document frequency \(n(c,t,w^{(c)})\) is much higher when bursting.
We empirically set \(\mu_0\) as the moving average \(\mu_0^{(t)}=\frac{1}{T}\sum_{\tau=t-T}^{t-1}n(c,\tau,w^{(c)})\), and set T=10.
Hence, at time \(t\), bursty or not is determined by comparing the probabilities of above poisson distributions. 
After bursty detection on the time series, we add each time \(t\)'s bursty word \(w^{(c)}\) into the set of event's candidate words \(\mathcal{B}_{c,t}\).

\textbf{Generating event phrases}.

\textbf{Linking event tweets with event phrases}.

%Text stream evolves more quickly with time than knowledge base.
%For example, recent state of Military contain .
%In other words, recent state is history-state-like topic timestamp.%在时间轴上的横截面。
